Investigations of the galaxies of the LCV

### 2023-03-23 paper.tex
first draft
- Added the hopefully final form of the project
- I have added almost all of the graphs
- i have created some scripts to automate writing in latex from python

% Created 2023-03-15 Wed 11:50
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{breakcites}
\usepackage{apacite}
\usepackage{paralist}
\usepackage{biblatex}
\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
\usepackage{hyperref}
\let\itemize\compactitem
\let\description\compactdesc
\let\enumerate\compactenum
\addbibresource{/bibl/bibliography/bibliography.bib}
\author{Dimitrios Papachistopoulos}
\date{\today}
\title{Finding the normalization constant of \(SFR_{del}\) and the relations between the various masses of the Galaxies}
\hypersetup{
 pdfauthor={Dimitrios Papachistopoulos},
 pdftitle={Finding the normalization constant of \(SFR_{del}\) and the relations between the various masses of the Galaxies},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6.1)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

\#\#+\LaTeX{}\textsubscript{HEADER}: \affiliation{Dr. Pavel Kroupa}
\begin{ABSTRACT}

@@

\noindent\rule{\textwidth}{0.5pt}
\end{ABSTRACT}
\tableofcontents

\section{The Galaxies in the Local Cosmological Volume (LCV)}
\label{sec:org776cf02}

The Catalogue of Neigbouring Galaxies (Karachentsev, Igor D. and Makarov  et al. 2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database \cite{CatalogLVGalaxies} are used to extract the K-band luminosities, the types of the galaxies, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of
\(\approx 11\) Mpc. The SFR values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248. From the remaing galaxies we have

@@

\section{Types of galaxies}
\label{sec:org3f06310}

@@

\section{Calculation of the normalization constant}
\label{sec:orgbfb382e}

@@

\subsection{Constant \(t_{sf}\)}
\label{sec:org4bfffb4}
The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr (e.g. Knox, Hawkins \& Hambly 1999), so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}). After that the equation of ratio

@@

\subsection{Constant \(\tau\)}
\label{sec:org3e5bf87}
Assuming for an constant \(\tau=3.5\) Gyr, we cannot use the same \(\overline{SFR}\) and ratio. Using the equations\textasciitilde{}(\Ref{eq:av_SFR M*}) and (\Ref{eq:ratio})

@@

The \(x_i\) results are more inline with the expected values from Kroupa et al. 2020 \(2.7<x<3.4\)
\begin{center}
\includegraphics[width=.9\linewidth]{./graphs/x-x_i.png}
\end{center}

\begin{center}
\includegraphics[width=.9\linewidth]{./graphs/A-A_del.png}
\end{center}

@@

\subsubsection{{\bfseries\sffamily TODO} DO sigma clipping for x to see if the x's are in agreement with the theoritical values}
\label{sec:org33fabf5}

\section{Mass relations}
\label{sec:orgcb5272f}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logMt.png}
\caption{\label{Total Mass - Stellar Mass}Total Mass - Stellar Mass: \(R^2=0.93\)}
\end{figure}

@@

\section{Calculate the gas depletion timescale \(\tau_g\)}
\label{sec:orgf5cea8c}

The gas depletion timescale τg measures the time taken by a galaxy to exhaust its gas content Mg given the current SFR (Pflamm-Altenburg \& Kroupa 2009).
$$
\tau_g=\frac{M_g}{\dot{M_*}}=\frac{M_g}{SFR}
$$
\end{document}

>>>>

% Created 2023-03-20 Mon 22:04
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{breakcites}
\usepackage{apacite}
\usepackage{paralist}
\usepackage{biblatex}
\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
\usepackage{hyperref}
\let\itemize\compactitem
\let\description\compactdesc
\let\enumerate\compactenum
\author{Dimitrios Papachistopoulos}
\date{\today}
\title{Investigations of the galaxies of the LCV}
\hypersetup{
 pdfauthor={Dimitrios Papachistopoulos},
 pdftitle={Investigations of the galaxies of the LCV},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6.1)}, 
 pdflang={English}}
\begin{document}

\maketitle
\begin{ABSTRACT}

@@

\noindent\rule{\textwidth}{0.5pt}
\end{ABSTRACT}

\section{The Galaxies in the Local Cosmological Volume (LCV)}
\label{sec:org630e55f}

The Catalogue of Neigbouring Galaxies (Karachentsev, Igor D. and Makarov  et al. 2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' databas\autocite{CatalogLVGalaxies}  are used to extract the K-band luminosities, the types of the galaxies, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of
\(\approx 11\) Mpc. The SFR values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248. From the remaing galaxies we have

@@

\section{Types of galaxies}
\label{sec:org6287ff6}

@@

\section{Calculation of the normalization constant}
\label{sec:orgbe376f2}

@@

\subsection{Constant \(t_{sf}\)}
\label{sec:org2e54374}
The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr (e.g. Knox, Hawkins \& Hambly 1999), so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}). After that the equation of ratio

@@

\subsection{Constant \(\tau\)}
\label{sec:orgce62d74}
Assuming for an constant \(\tau=3.5\) Gyr, we cannot use the same \(\overline{SFR}\) and ratio. Using the equations\textasciitilde{}(\Ref{eq:av_SFR M*}) and (\Ref{eq:ratio})

@@

The \(x_i\) results are more inline with the expected values from Kroupa et al. 2020 \(2.7<x<3.4\)
\begin{center}
\includegraphics[width=.9\linewidth]{./graphs/x-x_icolor_color.png}
\end{center}

The galaxies with low x and x\textsubscript{i}, have a lower color index (\(<B-V>\)) then galaxies with higher x, which means that they are younger galaxies, as expected by the x values. For example, if x has a value of 1 \(\Leftrightarrow x_i=2\) then

\begin{center}
\includegraphics[width=.9\linewidth]{./graphs/log_A_del-log_A.png}
\end{center}

@@

\subsubsection{{\bfseries\sffamily TODO} DO sigma clipping for x to see if the x's are in agreement with the theoritical values}
\label{sec:org0b0321d}

\section{Mass relations}
\label{sec:org70c9aab}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logMtcolor_log_Mass_ratio.png}
\caption{\label{Total Mass - Stellar Mass}Total Mass - Stellar Mass: \(R^2=0.93\)}
\end{figure}
\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logMtcolor_log_SFR_0.png}
\caption{\label{Total Mass - Stellar Mass}Total Mass - Stellar Mass: \(R^2=0.93\)}
\end{figure}
\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logMtcolor_log_tau_g.png}
\caption{\label{Total Mass - Stellar Mass}Total Mass - Stellar Mass: \(R^2=0.93\)}
\end{figure}

@@

\section{Calculate the gas depletion timescale \(\tau_g\)}
\label{sec:orgaf32583}

The gas depletion timescale τg measures the time taken by a galaxy to exhaust its gas content Mg given the current SFR (Pflamm-Altenburg \& Kroupa 2009).
$$
\tau_g=\frac{M_g}{\dot{M_*}}=\frac{M_g}{SFR}
$$

\printbibliography
\end{document}
